THE ROLE OF DISK VOLATILE CHEMISTRY AND DYNAMICS IN SHAPING THE COMPOSITIONS OF NASCENT PLANETS

### 2017-07-01 Postdoc Applications/NPP_proposal.tex
upd

The pioneering work of [10], as well as the purported detection of a superstellar gas-phase C/O ratio in the atmosphere of WASP 12-b [11], inspired further theoretical investigations into the C/O ratio in disk and planet atmospheres. The model of [11] assumes a static disk, thus ignoring disk chemistry or dynamics. In reality, however, there are many chemical and dynamical processes that occur in disks (see [9] for a review), which will change the chemical molecular and elemental abundances, and therefore C/O ratios. For example, [12] calculate the C/O ratio throughout the disk including dynamical effects such as radial drift, grain coagulation, and the diffusion of volatile vapors. [13] include planetary migration in their C/O ratio calculation, and use the C/O ratio to constrain migration mechanisms. Additional carbon volatile carriers, such as CH$_4$, are considered by [14],  and they find that the gas-phase C/O ratio may be enriched by up to a factor of four compared to the Solar value in the outer disk.  While the C/O ratio is an important signature of disk and planet atmospheric chemistry, many other compounds have been detected in disks [9], which may affect the composition of disks and of nascent planets even when only dynamical processes are included and the chemistry is static, such as in the studies described above.

@@

\begin{figure}[h!]
\centering
\includegraphics[width=0.8\textwidth]{C_O_water_ice.pdf}
%\vspace{-0.5in}
\caption{C/O ratio estimates in gas (solid lines) and dust (dashed lines) as function of semimajor axis in a viscous disk, for CO as pure ice (top panel) or as water dominated ices (bottom panel). The H$_2$O, CO$_2$ and CO snowlines are shown for particles with initial sizes $\sim0.05$ cm $\lesssim s \lesssim$ 7 m as indicated by the color bar. The C/O ratio in a static disk (black lines) is shown for comparison. Taken together, disk dynamics and ice compositions move the CO snowline inward by a factor of $\sim$7. From [17].} 
\label{fig:CO_ratio}
\end{figure}

@@

3. The results of my planet synthesis study will provide a robust framework of using a planet's composition as a tracer of its formation location. Furthermore, comparing my results with current observations of atmospheric spectra (e.g., Figure 3 from $[4]$), and more importantly future JWST observations, will lead to great scientific strides in understanding the complex connection between protoplanetary disks and the formation, evolution and composition of exoplanets.

\begin{figure}[h!]
\centering
\vspace{-0.2in}
\includegraphics[width=\textwidth]{water_spectrum}
\vspace{-0.2in}
\caption{The transmission spectrum of exoplanet WASP-12b measured with the Hubble Space Telescope/Wide Field Camera 3. The white dots are the measured transit depths, the blue squares and dark blue line are the best fit model, while the shaded regions represent 1- and 2 $\sigma$ intervals in the retrieved spectrum. The increase in transit depth around $\sim$1.4 $\mu$m is evidence for a water feature in the atmosphere (from $[4]$).}
\label{fig:HLTau}
\end{figure}

>>>>

The pioneering work of [10], as well as the purported detection of a superstellar gas-phase C/O ratio in the atmosphere of WASP 12-b [11], inspired further theoretical investigations into the C/O ratio in disk and planet atmospheres. The model of [10] assumes a static disk, thus ignoring disk chemistry or dynamics. In reality, however, there are many chemical and dynamical processes that occur in disks (see [9] for a review), which will change the chemical molecular and elemental abundances, and therefore C/O ratios. For example, [12] calculate the C/O ratio throughout the disk including dynamical effects such as radial drift, grain coagulation, and the diffusion of volatile vapors. [13] include planetary migration in their C/O ratio calculation, and use the C/O ratio to constrain migration mechanisms. Additional carbon volatile carriers, such as CH$_4$, are considered by [14],  and they find that the gas-phase C/O ratio may be enriched by up to a factor of four compared to the Solar value in the outer disk.  While the C/O ratio is an important signature of disk and planet atmospheric chemistry, many other compounds have been detected in disks [9], which may affect the composition of disks and of nascent planets even when only dynamical processes are included and the chemistry is static, such as in the studies described above.

@@

\begin{figure}[h!]
\centering
\includegraphics[width=0.8\textwidth]{C_O_water_ice.pdf}
%\vspace{-0.5in}
\caption{C/O ratio estimates in gas (solid lines) and dust (dashed lines) as function of semimajor axis in a viscous disk, for CO as pure ice (top panel) or as water dominated ices (bottom panel). The H$_2$O, CO$_2$ and CO snowlines are shown for particles with initial sizes $\sim0.05$ cm $\lesssim s \lesssim$ 7 m as indicated by the color bar. The C/O ratio in a static disk (black lines) is shown for comparison. Taken together, disk dynamics and ice compositions move the CO snowline inward by a factor of $\sim$7. From [18].} 
\label{fig:CO_ratio}
\end{figure}

@@

3. The results of my planet synthesis study will provide a robust framework of using a planet's composition as a tracer of its formation location. Furthermore, comparing my results with current observations of atmospheric spectra (e.g., Figure 6), and more importantly future JWST observations, will lead to great scientific strides in understanding the complex connection between protoplanetary disks and the formation, evolution and composition of exoplanets.

\begin{figure}[h!]
\centering
\vspace{-0.2in}
\includegraphics[width=\textwidth]{water_spectrum}
\vspace{-0.2in}
\caption{The transmission spectrum of exoplanet WASP-12b measured with the Hubble Space Telescope/Wide Field Camera 3. The white dots are the measured transit depths, the blue squares and dark blue line are the best fit model, while the shaded regions represent 1- and 2 $\sigma$ intervals in the retrieved spectrum. The increase in transit depth around $\sim$1.4 $\mu$m is evidence for a water feature in the atmosphere. From $[4]$.}
\label{fig:HLTau}
\end{figure}
